---
title: "UVC datasets - exploring monitoring structure and herbivore assemblages"
output:
  pdf_document: default
  html_notebook: default
---

```{r, echo=FALSE, include=FALSE, messages=FALSE}
# data loads and working directory stuff
setwd('/Users/robins64/Documents/git_repos/grazing-gradients')

## ** add working directories! **
#jan
#jeneen
#sam

# load tidy packages and set ggplot theme
library(tidyverse); theme_set(theme_bw()); library(gridExtra)

load('data/wio_gbr_herb_master.Rdata')
sey<-herb %>% filter(dataset=='Seychelles')

```


#### Seychelles

* Seychelles data are 7m radius point counts conducted at 21 reef sites in 1994, 2005, 2008, 2011, 2014, 2017. 
* Sites were stratified according to habitat (granite = 7, patch = 7, carbonate = 7) and management status (12 = fished, 9 = MPAs)
* Reefs are the inhabited Seychelles islands, Mahe and Praslin
* Useful papers describing dataset methods: Graham et al. 2015 (Predicting climate-driven regime shifts..., Nature)

Across all surveys, ```r length(unique(sey$species))``` herbivore species were recorded, which are composed of:

```{r, echo=F} 
# count number of unique species per functional group
aggregate(species ~ FG, sey, function(x) length(unique(x)))
```

Scrapers dominated herbivore assemblages on both fished and protected reefs, and browser biomass was slightly higher than grazer biomass after 1994 (i.e. after bleaching). High variability in browser biomass suggests that strong spatial variation in browser presence. This was less true for scrapers, for which biomass may be high at all reef sites. There was a weak protection effect apparent, with slightly higher biomass of all feeding groups in protected sites.

```{r, echo=F}

## estimate biomass gradient across management status 
biom<-sey %>%
		group_by(site, date, transect, FG, management) %>% 
		summarise(biom = sum(biomass.kgha)) %>%
		group_by(site, date, FG, management) %>%
		summarise(biom = mean (biom))

ggplot(biom, aes(date, log10(biom+1), fill=management)) + geom_boxplot() + facet_wrap(~FG)

```

Grazer size distributions indicated high abundance of small-bodied individuals. Scraper and browser sizes were more equitably distributed across the size range. Scrapers had the largest body sizes, with some individuals between 0.5-2 kg. 

```{r, echo=F, fig.caption = 'Herbivore size distribution at Seychelles'}
## estimate size distribution by functional groups
ggplot(sey, aes(log(mass.g, 2), fill=FG)) + geom_histogram(breaks=c(1:10)) + facet_wrap(management~FG) + theme(legend.position='none') + scale_x_continuous(breaks=c(1:10), labels=c(2^c(1:10))) + labs (x='Mass (g)')
```

**Common herbivore species**

Considering common species as those that were observed frequently (i.e. high detection rate at replicate UVC level) and those that are high in abundance or biomass (i.e. mean biomass across UVC replicates at each site).

```{r, echo=F, fig.caption = 'Common herbivores in Seychelles', fig.width=3, fig.height=10}

## estimate detection frequency by species
detect <- sey %>% group_by(unique.id, species, FG) %>% 
          summarise(freq = n()) %>% ## total detections per UVC replicate
          group_by(species, FG) %>%
          summarise(freq = mean(freq))  ## mean detection by species

## estimate mean abundance at site level, by species
abund <- sey %>% group_by(unique.id, site, species, FG) %>% 
        summarise(abund = sum(abundance.500m2)) %>% ## total abundance per UVC
        group_by(species, FG) %>% 
        summarise(abund = mean(abund)) ## mean abundance per site

## estimate mean biomass at site level, by species
biom <- sey %>% group_by(unique.id, site, species, FG) %>% 
        summarise(biom = sum(biomass.kgha)) %>% ## total biomass per UVC
        group_by(species, FG) %>% 
        summarise(biom = mean(biom)) ## mean biomass per site

g1<-ggplot(detect, aes(x=reorder(species,freq), y= freq, fill=FG)) +    geom_bar(stat='identity') +  
  labs(y='Frequency of occurrence', x='', title='Seychelles: abundance/biomass distributions') +
  coord_flip() + theme(legend.position='none')
  
g2<-ggplot(abund[abund$abund<100,], aes(reorder(species,abund), abund, fill=FG)) + 
  geom_bar(stat='identity') + 
  labs(y='Mean abundance per 500m2', x='') +
  coord_flip() + theme(legend.position='none')

g3<-ggplot(biom[biom$biom<300,], aes(reorder(species,biom), biom, fill=FG)) + 
  geom_bar(stat='identity') + 
  labs(y='Mean biomass kg ha-1', x='') +
  coord_flip() + theme(legend.position=c(0.75, 0.25))
  
grid.arrange(g1, g2, g3)



```


#### Maldives



#### GBR



#### Chagos