---
title: "UVC datasets - exploring monitoring structure and herbivore assemblages"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---

```{r, echo=FALSE, include=FALSE, messages=FALSE}

# load tidy packages and set ggplot theme
library(tidyverse); theme_set(theme_bw()); library(gridExtra)

# data loads
load('data/wio_gbr_herb_master.Rdata')
sey<-herb %>% filter(dataset=='Seychelles')

```


#### Seychelles

* Seychelles data are 7m radius point counts conducted at 21 reef sites in 1994, 2005, 2008, 2011, 2014, 2017. 
* Sites were stratified according to habitat (granite = 7, patch = 7, carbonate = 7) and management status (12 = fished, 9 = MPAs)
* Reefs are the inhabited Seychelles islands, Mahe and Praslin
* Useful papers describing dataset methods: Graham et al. 2015 (Predicting climate-driven regime shifts..., Nature)

Across all surveys, ```r length(unique(sey$species))``` herbivore species were recorded, which are composed of:

```{r, echo=F} 
# count number of unique species per functional group
aggregate(species ~ FG, sey, function(x) length(unique(x)))
```

Scrapers dominated herbivore assemblages on both fished and protected reefs, and browser biomass was slightly higher than grazer biomass after 1994 (i.e. after bleaching). High variability in browser biomass suggests that strong spatial variation in browser presence. This was less true for scrapers, for which biomass may be high at all reef sites. There was a weak protection effect apparent, with slightly higher biomass of all feeding groups in protected sites.

```{r, echo=F}

## estimate biomass gradient across management status 
biom<-sey %>%
		group_by(site, date, transect, FG, management) %>% 
		summarise(biom = sum(biomass.kgha)) %>%
		group_by(site, date, FG, management) %>%
		summarise(biom = mean (biom))

ggplot(biom, aes(date, log10(biom+1), fill=management)) + geom_boxplot() + facet_wrap(~FG)

```

Grazer size distributions indicated high abundance of small-bodied individuals. Scraper and browser sizes were more equitably distributed across the size range. Scrapers had the largest body sizes, with some individuals between 0.5-2 kg. 

```{r, echo=F, fig.caption = 'Herbivore size distribution at Seychelles'}
## estimate size distribution by functional groups
ggplot(sey, aes(log(mass.g, 2), fill=FG)) + geom_histogram(breaks=c(1:10)) + facet_wrap(management~FG) + theme(legend.position='none') + scale_x_continuous(breaks=c(1:10), labels=c(2^c(1:10))) + labs (x='Mass (g)')
```

**Common herbivore species**

Considering common species as those that are high in abundance or biomass (i.e. mean biomass across UVC replicates at each site).

```{r, echo=F, fig.caption = 'Common herbivores in Seychelles', fig.width=6, fig.height=10}

## estimate mean abundance at site level, by species
abund <- sey %>% group_by(unique.id, site, species, FG) %>% 
        summarise(abund = sum(abundance.500m2)) %>% ## total abundance per UVC
        group_by(species, FG) %>% 
        summarise(abund = mean(abund)) ## mean abundance per site

## estimate mean biomass at site level, by species
biom <- sey %>% group_by(unique.id, site, species, FG) %>% 
        summarise(biom = sum(biomass.kgha)) %>% ## total biomass per UVC
        group_by(species, FG) %>% 
        summarise(biom = mean(biom)) ## mean biomass per site

g2<-ggplot(abund[abund$abund<100,], aes(reorder(species,abund), abund, fill=FG)) + 
  geom_bar(stat='identity') + 
  labs(y='Mean abundance per 500m2', x='',title='Seychelles: abundance/biomass distributions') +
  coord_flip() + theme(legend.position='none', axis.text.y=element_text(size=6))

g3<-ggplot(biom[biom$biom<300,], aes(reorder(species,biom), biom, fill=FG)) + 
  geom_bar(stat='identity') + 
  labs(y='Mean biomass kg ha-1', x='') +
  coord_flip() + theme(legend.position=c(0.75, 0.25), axis.text.y=element_text(size=6))
  
grid.arrange(g2, g3)



```


#### Maldives
* 11 sampled sites
* 4 transects each site of 250 m^2 (most) or 100 m^2 area
* 1 depth level (8m)
* 1 management level (Fished)
* 1 habitat level (Exposed)
* 30 herbivore species (3 browser spp., 13 grazer spp., 14 scraper spp.)
* 7 herbivore families
* site, biomass, FG, species only variables of interest





#biomass ditribution across functional groups
```{r, echo=F, fig.caption = 'Herbivore size distribution in Maldives'}

#package loads
library(ggplot2)
library(tidyverse)
library(gridExtra)

# data loads
load('data/wio_gbr_herb_master.Rdata')
maldives <- herb %>% filter(dataset=='Maldives')

ggplot(maldives, aes(log(mass.g, 2), fill=FG)) + geom_histogram(breaks=c(1:10)) + 
  facet_wrap(~FG) + theme(legend.position='none') + scale_x_continuous(breaks=c(1:10), 
  labels=c(2^c(1:10))) + labs (x='Mass (g)')

```
*Browsers few but large, grazers smaller but many, scrapers more equally spread in both

#common herbivore species


```{r, echo=F, fig.caption = 'Common herbivores in Maldives', fig.width=6, fig.height=10}

#cheeky James script steal - good deal 1
abund.mal <- maldives %>% group_by(unique.id, site, species, FG) %>% 
        summarise(abund.mal = sum(abundance.500m2)) %>%
        group_by(species, FG) %>% 
        summarise(abund.mal = mean(abund.mal))

#good deal 2
biom.mal <- maldives %>% group_by(unique.id, site, species, FG) %>% 
        summarise(biom.mal = sum(biomass.kgha)) %>%
        group_by(species, FG) %>% 
        summarise(biom.mal = mean(biom.mal))

gooddeal1<-ggplot(abund.mal[abund.mal$abund.mal<100,], aes(reorder(species,abund.mal), abund.mal, fill=FG)) + 
  geom_bar(stat='identity') + 
  labs(y='Mean abundance per 500m2', x='',title='Maldives: abundance/biomass distributions') +
  coord_flip() + theme(legend.position='none', axis.text.y=element_text(size=6))

gooddeal2<-ggplot(biom.mal[biom.mal$biom.mal<300,], aes(reorder(species,biom.mal), biom.mal, fill=FG)) + 
  geom_bar(stat='identity') + 
  labs(y='Mean biomass kg ha-1', x='') +
  coord_flip() + theme(legend.position=c(0.75, 0.25), axis.text.y=element_text(size=6))
  
grid.arrange(gooddeal1, gooddeal2)



```

#### GBR



#### Chagos

```{r, echo=FALSE, include=FALSE, messages=FALSE}
#Load data and filter for chagos
load("data/wio_gbr_herb_master.Rdata")
str(herb) ## check structure of data frame
unique(herb$dataset) ## check regions in herb
chagos <- herb[herb$dataset == 'Chagos',]
write.csv(chagos, file = 'data/chagos_master.csv')
chagos$FG <- as.factor(chagos$FG)
levels(chagos$FG)
```

```{r, echo=FALSE, include=FALSE, messages=FALSE}

#Load packages
library(tidyverse)
library (ggplot2)
library(gridExtra)
```

*Exploring the data*

```{r, echo=FALSE, include=FALSE, messages=FALSE}
#Get some descriptive info on survey data
summary(chagos) #5729 records
#Number of sites
chagos$site <- as.factor(chagos$site)
levels(chagos$site) #20 sites
#Number of reefs
chagos$reef <- as.factor(chagos$reef) #4 reefs
#Number of transects per site
chagos$transect <- as.factor(chagos$transect) #1-4 transects
chagos %>% count(site, transect, sort =TRUE)
#Number of sitings of each species
chagos$species <- as.factor(chagos$species)
chagos %>% count(species) # 52 species


#From James
# count number of unique species per functional group
aggregate(species ~ FG, chagos, function(x) length(unique(x)))
```
Chagos dataset: total of 52 species, 5729 records, across 20 sites at 4 reefs, with between 1-4 transects at each site.


```{r, echo=F}
#From James script
# count number of unique species per functional group
aggregate(species ~ FG, chagos, function(x) length(unique(x)))
```
Very few browser species (5) as compared to grazers (22) and scrapers (25)... but there are some duplicate species due to typos, so still need to clean that up.


```{r, echo=F}
#From James script
## estimate size distribution by functional groups
ggplot(chagos, aes(log(mass.g, 2), fill=FG)) + geom_histogram(breaks=c(1:10)) + facet_wrap(management~FG) + theme(legend.position='none') + scale_x_continuous(breaks=c(1:10), labels=c(2^c(1:10))) + labs (x='Mass (g)')



#ddply(chagos, .(FG), summarize,  MeanMass=mean(mass.g))
```
There are more grazers than any other functional group. Most grazers are mid-sized, whereas there are more large scrapers and browsers. The mean size of browzers is 1476g, grazers 115g, and scrapers 1808. 


Now need to look at abundance and biomass of species and functional groups across sites...

```{r, echo=F}
#From James' script
## estimate mean abundance at site level, by species
chagos$species <- as.character(chagos$species)
abund <- chagos %>% group_by(unique.id, site, species, FG) %>% 
        summarise(abund = sum(abundance.500m2))%>% ## total abundance per UVC
        group_by(species, FG) %>% 
        summarise(abund = mean(abund)) ## mean abundance per site

## estimate mean biomass at site level, by species
biom <- chagos %>% group_by(unique.id, site, species, FG) %>% 
        summarise(biom = sum(biomass.kgha)) %>% ## total biomass per UVC
        group_by(species, FG) %>% 
        summarise(biom = mean(biom)) ## mean biomass per site

g2<-ggplot(abund[abund$abund<100,], aes(reorder(species,abund), abund, fill=FG)) + 
  geom_bar(stat='identity') + 
  labs(y='Mean abundance per 500m2', x='',title='Chagos: abundance/biomass distributions') +
  coord_flip() + theme(legend.position='none', axis.text.y=element_text(size=6))

g3<-ggplot(biom[biom$biom<300,], aes(reorder(species,biom), biom, fill=FG)) + 
  geom_bar(stat='identity') + 
  labs(y='Mean biomass kg ha-1', x='') +
  coord_flip() + theme(legend.position=c(0.75, 0.25), axis.text.y=element_text(size=6))

grid.arrange(g2, g3)
```


```{r, echo=F}
#log scale biomass gradient
chagos$logbiomass <- log10(chagos$biomass.kgha)
ggplot(chagos, aes(x=logbiomass, fill=FG)) + geom_density(alpha=.3)
```

There are no dates recorded for the Chagos dataset, so no time series analyses could be done. Additionally, all of Chagos is "unfished". Therefore, only "depth" and "habitat" gradients were explored further to biomass. If lat long values can be attached to site names, a spatial look at the data can be done as well. 

```{r, echo=F}
#Comparing sheltered and unsheltered functional groups
#Grouped bar chart showing biomass of each FG at different habitats, blank is unrecorded habitat type
ggplot(chagos, aes(fill=FG, y=biomass.kgha, x=habitat)) +
  geom_bar(position="dodge", stat="identity")

```


```{r, echo=F, include=F}
#Comaparing depth at 3m and 9m
str(chagos) #change depth from numeric to character for graph
chagos$depth <- as.character(chagos$depth)
#Plot biomass of each FG at 3 and 9 m 
ggplot(chagos, aes(fill=FG, y=biomass.kgha, x=depth)) +
  geom_bar(position="dodge", stat="identity")
```


