---
title: "Models 5 - Herbivore function linear models"
output:
  html_document:
    df_print: paged
    fig_width: 7
    fig_height: 6
    fig_caption: true
    css: style.css
    theme: sandstone
  html_notebook: default
  pdf_document: default
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H')  ## Hold figure positions

## scraper functions
load(file = '../../results/models/scraper_function.Rdata'); scrape<-h

## grazer functions
load(file = '../../results/models/cropper_function.Rdata'); crop<-h

library(ggplot2); library(visreg); library(lme4); library(tidyverse); library(scales); library(sjPlot); 
library(funk); library(cowplot)
theme_set(theme_sleek())
options(scipen=999)
library(wesanderson); pal <- wes_palette("Zissou1", 21, type = "continuous")
cols<-c(pal[5], pal[12], pal[18], pal[1], pal[15],pal[21] )

```

This document loads grazing function estimates for croppers and scrapers, then fits linear mixed effects models that measure the relative effects of benthic and fishing covariates (the same as 01_biomass_models.Rmd).

function ~ fixed(hard.coral + macroalgae + complexity + substrate + rubble + fishbiom + fished + pristine) + random(dataset/reef)

<br><br>

\newpage

#### Croppers

<br><br>

```{r, include=FALSE}

## scale vars to keep covariate means = 0. This is helpful for comparing effect sizes when covariates are on different scales.
h<-crop
h$hard.coral <- scale(h$hard.coral)
h$macroalgae <- scale(h$macroalgae)
h$complexity <- scale(h$complexity)
h$rubble <- scale(h$rubble)
h$substrate <- scale(h$substrate)
h$fish.biom <- scale(h$fish.biom)

## make dummy variables
h$fish.dummy<-ifelse(h$management=='Fished', 1, 0)
h$pristine.dummy<-ifelse(h$management=='Unfished', 1, 0)
# we use 2 dummy variables for 3 levels

## match in site level diversity/size predictors
load(file = '../../results/cropper_attributes.Rdata')
h$site.richness<-scale(diversity.preds$richness[match(h$unique.id, diversity.preds$unique.id)])
h$site.size<-scale(diversity.preds$mean.size[match(h$unique.id, diversity.preds$unique.id)])


## drop 0 grazer site
#h<-h[h$grazer > 0,]

m.grazer<-glmer(cropping.gram.ha ~ hard.coral + macroalgae + rubble + substrate + complexity + fish.biom + fish.dummy + pristine.dummy + ## fixed
  site.richness + site.size +
          (1 | dataset/reef) , ## random, nested = reefs within datasets
                data = h, family='Gamma'(link='log'))

# save modelled dataframe as 'focal'
focal<-h

save(focal, m.grazer, file = '../../results/models/function_m_croppers.Rdata')

```

```{r, echo=FALSE, include=TRUE, messages=FALSE, fig.align = 'center', fig.cap='Figure 1: Cropper model diagnostics - residuals and fitted values'}
print(summary(m.grazer),  digits = 2, signif.stars = FALSE)

print(paste('R-squared = ', piecewiseSEM::rsquared(m.grazer)))

## model diagnostic plots - grazer biomass
par(mfrow=c(2,2), mar=c(5,4,2,2))
hist(resid(m.grazer), main = 'model residuals', xlab='Residuals', cex.main=0.8)
plot(resid(m.grazer), fitted(m.grazer), xlab='Residuals', ylab= 'Fitted values', pch=16,col=alpha('black', 0.5), cex.main=0.8)
plot(resid(m.grazer), h$cropping.gram.ha, xlab='Residuals', ylab= 'Observed function', pch=16,col=alpha('black', 0.5), cex.main=0.8)
plot(predict(m.grazer, type='response'), h$cropping.gram.ha, xlab='Predicted function', ylab='Observed function', pch=16, col=alpha('black', 0.5), cex.main=0.8)
```

<br><br>
<br><br>

```{r, echo=FALSE, include=TRUE, messages=FALSE, fig.align = 'center', fig.cap='Figure 2: Cropper model predictions'}
plot_models(m.grazer)
```


\newpage

#### Scrapers
<br><br>

```{r, include=FALSE}

## scale vars to keep covariate means = 0. This is helpful for comparing effect sizes when covariates are on different scales.
h<-scrape
h$hard.coral <- scale(h$hard.coral)
h$macroalgae <- scale(h$macroalgae)
h$complexity <- scale(h$complexity)
h$rubble <- scale(h$rubble)
h$substrate <- scale(h$substrate)
h$fish.biom <- scale(h$fish.biom)

## make dummy variables
h$fish.dummy<-ifelse(h$management=='Fished', 1, 0)
h$pristine.dummy<-ifelse(h$management=='Unfished', 1, 0)
# we use 2 dummy variables for 3 levels

## match in site level diversity/size predictors
load(file = '../../results/scraper_attributes.Rdata')
h$site.richness<-scale(diversity.preds$richness[match(h$unique.id, diversity.preds$unique.id)])
h$site.size<-scale(diversity.preds$mean.size[match(h$unique.id, diversity.preds$unique.id)])


## drop 0 grazer site
#h<-h[h$grazer > 0,]

m.scraper<-glmer(scraping ~ hard.coral + macroalgae + rubble + substrate + complexity + fish.biom + fish.dummy + pristine.dummy + ## fixed
  site.richness + site.size +
          (1 | dataset/reef) , ## random, nested = reefs within datasets
                data = h, family='Gamma'(link='log'))

# save modelled dataframe as 'focal'
focal<-h

save(focal, m.scraper, file = '../../results/models/function_m_scrapers.Rdata')

```

```{r, echo=FALSE, include=TRUE, messages=FALSE, fig.align = 'center', fig.cap='Figure 3: Scraping model diagnostics - residuals and fitted values'}
print(summary(m.scraper),  digits = 2, signif.stars = FALSE)

print(paste('R-squared = ', piecewiseSEM::rsquared(m.scraper)))

## model diagnostic plots - scraper biomass
par(mfrow=c(2,2), mar=c(5,4,2,2))
hist(resid(m.scraper), main = 'model residuals', xlab='Residuals', cex.main=0.8)
plot(resid(m.scraper), fitted(m.scraper), xlab='Residuals', ylab= 'Fitted values', pch=16,col=alpha('black', 0.5), cex.main=0.8)
plot(resid(m.scraper), h$scraping, xlab='Residuals', ylab= 'Observed function', pch=16,col=alpha('black', 0.5), cex.main=0.8)
plot(predict(m.scraper, type='response'), h$scraping, xlab='Predicted function', ylab='Observed function', pch=16, col=alpha('black', 0.5), cex.main=0.8)
```

```{r, echo=FALSE, include=TRUE, messages=FALSE, fig.align = 'center', fig.cap='Figure 4: Scraping model predictions'}
plot_models(m.scraper)
```