---
title: ""
output: html_document
bibliography: grazer-library.bib
csl: coral-reefs.csl
---

Title: Herbivore biomass decouples from grazing function along benthic and fishing gradients

Authors:

Affiliations: 

```{r, echo=F, include=T, message=F}
library(knitcitations); library(bibtex); library(citr)	
```

#### Introduction

Species have certain functions that do good things, such as this and that. But functions are difficult to measure, often requiring small-scale, data-intensive approaches that quantify both individual behaviours and population sizes. Given that anthropogenic pressures are degrading and changing ecosystem functions over large spatial scales, there is a critical need to assess how functional approaches can be applied at a macroecological extent.

<!-- I had a hard time envisioning how this first paragraph would go, maybe it would be better to focus on herbivory in general is an important driver of habitat regime shifts, how it varies across different functional groups, how it can be impacted by humans? Then we can start off with more general examples including from other systems like forests, plants, kelp forests and salt marsh communities? Or even starting off with how consumers control communtity structure and ecosystem function? Or I just had a hard time picturing it because I wasn't at the meeting where you guys talked about it :) -->

<!-- Good points, thanks Jamie. Like you say, I think the opener should be about herbivory ~ habitat effects, harvesting by humans, and regime shifts. Then show our understanding of herbivory functions tend to be small scale functional ecology, but that these patterns (harvesting, habitat change) play out at macroscales. Thus, there is a need to combined functional ecology and macroecology. Similar intro to a new paper in Global Ecol. & Biogeogr (Longo et al. 2018, 'Trophic interactions...'), have a look.-->


​	On tropical coral reefs, top-down control of algae and promotion of calcifying coral taxa are key functions primarily performed by herbivorous fishes [@Bellwood2004], REF). Several decades of feeding observations indicate that herbivorous fishes are comprised of three main functional roles defined by their feeding morphology and behaviours: cropping, scraping and browsing [@Bellwood1990, @Polunin1995, @Green2009]. Cropping species graze filamentous turf algae and promote coral settlement and growth by maintaining cropped algal states (REF). Scraping parrotfish graze dead coral substrate to consume detritus and endolithial material, with larger species further defined as excavators, targeting live coral and removing larger portions of hard substrate [@Bonaldo2014, @Russ2015]. Browsing species are macroalgal specialists, thus less directly linked to coral dominance, but feed on established fleshy algal taxa [@Chong-Seng2014], potentially reverting macroalgal-dominated to coral-dominated states [@Bellwood2006]. Combined, these three grazing functions performed are considered essential for providing resistance to chronic background stressors and the maintenance of coral-dominated states [@Bellwood2004].

These different herbivore functional groups and thus their functions, are controlled by both benthic habitat changes and top down fishing pressure. Because algae can proliferate in the absence of grazing pressure [@Mumby2006a, @Burkepile2008], correlative analyses of fished reef ecosystems have identified grazing biomass thresholds below which reefs become algae dominated [@Graham2015, @Jouffray2015, @Robinson2018]. As herbivore populations are overexploited across the tropics [@Edwards2013], it is therefore implied that grazing functions are comprimised on inhabited reefs. However, fishing effects can be compounded by bottom-up structuring of herbivore assemblages [@Russ2015], whereby differences in habitat associations among individual taxa cause herbivore populations to vary among neigbouring habitat types <!-- i find this part of this sentence here confusing but i'm not sure how to change it -->[@Doropoulos2013] and reorganize in response to changes in benthic composition [@Gilmour2013]. For example, cropper and scraper biomass is maximised on reefs with intact coral architecture [@Heenan2016], but also on reefs with high availability of algal material and dead coral substrate [@Wilson2006, @Gilmour2013, @Robinson2018]. Grazing biomass of browsing species varies among reef zones of coral-dominated habitats [@Hoey2013] and, in seaweed habitats, shifts predictably with macroalgal density [@Hoey2011, @Robinson2018]. Thus, herbivore assemblage structure is mediated by both habitat composition and fishing intensity. Consequently, to understand how functional feeding groups are distributed at larger scales, such as across reef regions, we must disentangle bottom-up processes from disrupting anthropogenic influences such as fishing. This analysis could then be used to infer constraints on grazing function under different scenarios of habitat degradation and fishing pressure.

<!-- I think for the above paragraph the topic sentence doesn't illustrate what the rest of the paragraph is talking about. The rest of the paragraph talks more about different factors that structure these different herbivore groups: primarily bottom up habitat forces and top down fishing forces. I would put the first two sentences as the last sentences for the first paragraph, and then add a new sentence maybe something like: These different herbivore functional groups and thus their functions, are controlled by both benthic habitat changes and top down fishing pressure. Because the first paragraph is talking about top down control of algae. -->

<!-- Done. Good points -->

	Patterns in herbivore biomass are widely used to imply changes in herbivore functioning on coral reefs [@Nash2015, @Robinson2018]. However, biomass data overlooks size- and species-specific differences in feeding roles (REF), and can be improved by integrating information on feeding rates to estimate grazing processes [@Bellwood1990, @Bellwood2003]. For example, habitat-mediated shifts in the structure of parrotfish assemblages correspond to shifts in rates of bioerosion, turf grazing, and coral predation [@Hoey2008], while high sediment loads can suppress feeding activity of grazers [@Goatley2012, @Goatley2016]. Because feeding rates scale allometrically with body size [@Lokrantz2008, @Nash2013], the functional role provided by larger individuals is disproportionately larger [@Bonaldo2008]. Thus, grazing function is even more susceptible to fishing pressure as larger individuals and species are highly vulnerable when fishing is size selective [@Edwards2013, @Taylor2014]. In the Indo-Pacific, exploitation of scraping and excavating parrotfish has been linked to declines in bioerosion rates [@Bellwood2003, @Bellwood2011), although grazing functions of smaller cropper and browser species do not appear to be impacted by fishing (REF). For these species, habitat effects on functioning may supersede fishing, but these effects have not been tested together.

​	Accounting for size- and species-differences in grazing rates can improve correlative models of grazing, benthic community composition, and fishing [@Mumby2006a, @Steneck2018], because benthic habitat effects (bottom-up) or fishing effects (top-down) can influence species composition and size structure. Therefore, biomass may be a poor proxy for functioning, particularly if habitat change or fishing alters herbivore biomass distributions and cause biomass ~ function relationships to become decoupled. Decoupling may be particularly problematic for large-scale correlative analyses that encompass diverse reefs with substantial variation in fishing intensity and habitat composition. Despite the critical role of herbivory in shaping reef condition (REF), the direction and strength of biomass ~ function relationships under different habitat and fishing pressure remains unmeasured. 

	Here, we combine underwater visual census (UVC) data with herbivore feeding observations to assess the relationship between herbivory, benthic habitat and fishing intensity across coral reefs in the Indo-Pacific. We ask the questions 1) how does fishing pressure and benthic composition influence herbivore biomass across the three functional groups (i.e. croppers, scrapers, browsers?), 2) how well does herbivore biomass predict grazing function? and 3) does fishing pressure and benthic composition alter the relationship between herbivore biomass and function? We hypothesize X and Y. This large spatial scale analysis uses UVC data that was collected at reefs in four Indo-Pacific regions, spanning a benthic gradient from coral to macroalgal dominance and a fishing gradient spanning X-Y fishable biomass. Surveyed reefs include habitats that experienced macroalgal regime shifts after climate-driven coral bleaching [@Graham2015], and range in exploitation intensity from open-access fisheries to marine protected areas and near-pristine wilderness areas [@Graham2014]. We fitted linear mixed effects models to examine variation in the biomass of three major functional feeding groups (grazers, scrapers, browsers) along benthic and fishing gradients. By converting grazer biomass to three grazing functions (turf grazing intensity, bioerosion, macroalgal consumption) and refitting biomass predictive model structures, we assess potential decoupling of biomass from grazing function.

<!-- I added questions based off the introduction issue, but feel free to take out or modify. I think it would be good to put our hypotheses here as well! Maybe we could discuss these in a meeting? I also feel feel like we should emphasize more what is novel about this paper: large spatial scale? grazing functions? -->

<!-- Yes, definitely - I'm thinking macroecology meets functional ecology...how is it done now? (bellwood scraper papers), can we apply it to entire grazing communities? (probably not, but here's a first go). Let's get everyone on a meeting once I have the scraper function data -->




***

## Discussion points

***

Future reefs:

- benthic regimes likely non-coral dominated. What is herbivore function?
- fishing more important (^^ human population) and more reliant on low TLs. How does function shift ?

Caveats:

- benthic regimes. No information on turfs. These may be common regimes on bleached reefs (Goatley et al. (2016, Ecol Society)).

- importance of sediment (Tebbett et al. in press, Goatley, check w/ Bellwood lab outputs)

- functional differences within FGs leads to huge functional redundancy, espec. for browsers (Bellwood et al. 2009, Streit et al. 2015, Verges et al. 2015) (lots of herb ones?)

- temperature differences can change the identity of dominant browsers (Verges), while grazing intensity appears to increase with temperature (REF, REF, Longo et al. 2018). Although our sites spanned a relatively narrow temperature gradient (e.g.), we cannot discount temperature-linked shifts in grazing behaviour. 

- effectiveness of browsers in removing established macroalgae is unclear (Suchley et al. 2016), particularly when macroalgae reaches high densities (Hoey & Bellwood 2011).

Herbivore function metrics:

Huge variation in metrics used, and mass standardized bite rates are typical but not grounded in allometric scaling theory. For example, mass standardized bite rates may correlate strongly with raw bite rates (Longo et al. 2018), so it is unclear if mass corrections add resolution to simple biomass data.

If functional pressure is estimated with video observations, this either integrates available biomass (bites on substrate, more fish = more bites) or ignores foray distances of individual fish which swim out of the video frame (Nash et al. 2013). Clear need to unite these disparate approaches, and collinearity with biomass should always be assessed.


Cut text:

The use of grazer biomass as a proxy for grazing function ignores  (REF) particularly at large scales where the feeding observations required to convert biomass to functional rates are unavailable. 

Similarly, different species may perform different functional roles within the same group (Streit et al. 2015), while the degree of morphological, diet, and foraging specialization can vary significantly among related species (Bellwood et al. 2012 microniche paper, Brandl et al. 2015), to the extent that entire functions may be provided by a single species (Bellwood et al. 2006, Hoey & Bellwood 2009, Mouillot?). Such distinctions further confound the use of biomass as a proxy for function, in ways which we were unable to measure here.

#### References
 
```{r, echo=F, include=T, message=F}
## exporting session info for the supplementary material
sink(file = 'supplementary_material_sessioninfo.txt')
sessionInfo()
sink()
```
