---
title: ''
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  pdf_document:
  latex_engine: xelatex
fig_width: 20
html_document: default
fig_height: 6
word_document: default
fontsize: 12pt

---

## TITLE

*Authors*

```{r, echo=F}
## set up figcounter
i = 0
```

#### Supplementary Methods

&nbsp;

```{r, out.width = "480px", echo=F,fig.align='center'}
knitr::include_graphics("../../figures/FigureS1_scrape_size.pdf"); i = i + 1
```

**Figure S`r i` | Size effects on scraper bite rates (A) and bite area (B).** Lines indicate median posterior predictions with 95% certainty intervals, excluding species and genera effects, across the range of observed body sizes (total length, cm). Points are observed bite rates or bite areas coloured by genera. 

\newpage

```{r, out.width = "480px", echo=F,fig.align='center'}
knitr::include_graphics("../../figures/FigureS2_cropper_bites.pdf"); i = i + 1
```

**Figure S`r i` | Cropper bite rate predictions (A) and observed cropper function in UVC (B)** Predicted bite rates are median posterior predictions with 95% certainty intervals (A), and boxplots are site-level observed cropping function for each reef, coloured by UVC region.

\newpage

```{r, out.width = "480px", echo=F,fig.align='center'}
knitr::include_graphics("../../figures/FigureS3_browser_bites.pdf"); i = i + 1
```

**Figure S`r i` | Browser bite rate predictions (A) and observed browser function in UVC (B)** Predicted bite rates are median posterior predictions with 95% certainty intervals (A), and boxplots are site-level observed browsing function for each reef, coloured by UVC region.

\newpage

```{r, out.width = "480px", echo=F,fig.align='center'}
knitr::include_graphics("../../figures/FigureS4_scraper_bites.pdf"); i = i + 1
```

**Figure S`r i` | Scraper bite rate predictions (A) and observed scraping function in UVC (B)** Predicted bite rates are median posterior predictions with 95% certainty intervals (A), and boxplots are site-level observed scraping function for each reef, coloured by UVC region.

\newpage


Evenness effect on scraping function