---
title: ''
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  pdf_document:
  latex_engine: xelatex
fig_width: 20
html_document: default
fig_height: 6
word_document: default
fontsize: 12pt

---

## TITLE

*Authors*

```{r, echo=F}
## set up figcounter
i = 0
```

#### Supplementary Methods

&nbsp;

```{r, out.width = "480px", echo=F,fig.align='center'}
knitr::include_graphics("../../figures/FigureS1_scrape_size.pdf"); i = i + 1
```

**Figure S`r i` | Size effects on scraper bite rates (A) and bite area (B).** Lines indicate median posterior predictions with 95% certainty intervals, excluding species and genera effects, across the range of observed body sizes (total length, cm). Points are observed bite rates or bite areas coloured by genera. 

\newpage



Cropping bite species and range in function
Browsing bite species and range in function
Scraping bite species and range in function
Evenness effect on scraping function